%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Research Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
\cventry
{Research Associate} % Job title
{IntERLab, Asian Institute of Technology} % Organization
{Bangkok, Thailand} % Location
{May 2022 - Present} % Date(s)
{\begin{cvitems} % Description(s) of tasks/responsibilities
		\item {Conducted data analysis and research on data collected from deployed environmental sensors.}
		\item {Integrated multiple sensor modules (BME280, MHZ16, PMS7003, etc.) and communication modules (SimCom7600H, CMWX1ZZABZ, ESP32) into an IoT platform, developing a real-time remote sensor system for air quality monitoring using LoRaWAN, WiFi, and cellular communication.}
		\item {Designed and implemented a sensor fleet management application to streamline monitoring and data collection.}
		\item {Developed and deployed a scalable, multi-process, real-time system for collecting, and processing air quality sensor data.}
\end{cvitems}}

%---------------------------------------------------------
\cventry
{Research Consultant} % Job title
{IntERLab, Asian Institute of Technology} % Organization
{Bangkok, Thailand} % Location
{Feb. 2021 - Apr. 2022} % Date(s)
{\begin{cvitems} % Description(s) of tasks/responsibilities
		\item {Developed and tested software for ESP32-based sensor devices aimed at haze monitoring and forest fire detection.}
		\item {Contributed to the hardware design and testing of custom sensor boards tailored to environmental monitoring.}
		\item {Deployed and managed a private LoRaWAN network server for reliable sensor communication.}
		\item {Experiments and research on the capabilities and optimization of LoRaWAN technology.}
\end{cvitems}}

%---------------------------------------------------------
\cventry
{Student Research Assistant} % Job title
{IntERLab, Asian Institute of Technology} % Organization
{Bangkok, Thailand} % Location
{Mar. 2019 - Jan. 2021} % Date(s)
{\begin{cvitems} % Description(s) of tasks/responsibilities
		\item {Integrated LoRaWAN software stack into IoT air quality sensors for remote monitoring.}
		\item {Developed a Python-based LoRaWAN data server application for efficient data collection and transmission.}
		\item {Created a React Native mobile application for "BangPun: Distributed Ledger for Rural Communities", enabling blockchain-based solutions for rural development.}
\end{cvitems}}
\end{cventries}
