%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Skills}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Programming Languages} % Role
    {}
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {C, Python, JavaScript, C++, SQL, Bash}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Technologies \& Tools} % Role
    {} % Event
    {} % Location
    {} % Date(s)
    {
	\begin{cvitems} % Description(s)
		\item {\emph{Embedded Systems Development:} Experience in embedded systems development.}
		\item {\emph{Data Science \& Analytics:} Experience with data processing, statistical analysis, and visualization using tools like Python (pandas, NumPy, Matplotlib), and Jupyter notebooks.}
		\item {\emph{Microcontroller Programming:} Experience in low-level programming for microcontrollers (e.g., ESP32, STM32, ATTINY).}
		\item {\emph{Network Programming:} Experience in socket programming, protocols, and designing communication systems.}
		\item {\emph{Linux System Programming:} Strong background in developing system-level applications, scripting, and debugging in Linux environments.}
		\item {\emph{Web Development \& Deployment:} Experience in building and deploying full-stack web application.}
		\item {\emph{Docker \& Virtualization:} Experience in containerization and orchestration using Docker, and Docker Compose.}
		\item {\emph{Robot Operating System (ROS):} Experience in using ROS for robotics development, including sensor integration, control systems, and path planning.}
		\item {\emph{Machine Vision:} Experience in computer vision techniques using libraries like OpenCV for object detection, image processing, and automation.}
	\end{cvitems}
	}
\end{cventries}

