%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Software Engineering Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
\cventry
{Individual Consultant, Embedded Systems Developer} % Job title
{Regional Integrated Multi-Hazard Early Warning System (RIMES)} % Organization
{Remote} % Location
{2024} % Date(s)
{\begin{cvitems} % Description(s) of tasks/responsibilities
		\item {Prototyped and conducted feasibility studies on a LiDAR-based real-time river monitoring system.}
\end{cvitems}}

%---------------------------------------------------------
\cventry
{Freelancer} % Job title
{Freelance} % Organization
{Remote} % Location
{2017 - 2018} % Date(s)
{\begin{cvitems} % Description(s) of tasks/responsibilities
		\item {Developed a web-based issue ticketing system via SMS using Node.js, Express.js, Backbone.js, and MongoDB.}
		\item {Built a PHP Laravel-based website for resort.}
\end{cvitems}}

%---------------------------------------------------------
\cventry
{Software Engineer II} % Job title
{Ixia, Keysight Technologies} % Organization
{Kolkata, India} % Location
{Apr. 2015 - Jun. 2016} % Date(s)
{\begin{cvitems} % Description(s) of tasks/responsibilities
		\item {Contributed to the integration of HTTP/2 support for the BreakingPoint platform.}
		\item {Prototyped "BreakingPoint VE" using \href{https://www.dpdk.org/}{DPDK}, analyzing its feasibility and performance impact.}
		\item {Developed software virtualization for BitBlaster (L2 packet generator) and Routing Robot (L3 packet generator) modules, modeling FPGA hardware for "BreakingPoint VE."}
		\item {Deployed a Docker registry and automated Docker scripts for hosting and building development environment images for BreakingPoint.}
		\item {Mentored an intern in the development of an internal resource reservation web application using Django, AngularJS, and MySQL.}
\end{cvitems}}

%---------------------------------------------------------
\cventry
{Software Engineer I} % Job title
{Ixia, Keysight Technologies} % Organization
{Kolkata, India} % Location
{Jul. 2013 - Apr. 2015} % Date(s)
{\begin{cvitems} % Description(s) of tasks/responsibilities
		\item {Enhanced system stability by fixing critical bugs in the BreakingPoint platform.}
		\item {Contributed to the development of BreakingPoint VE, the virtualized version of the platform.}
		\item {Implemented various performance improvements for BreakingPoint VE to optimize its efficiency.}
\end{cvitems}}

%---------------------------------------------------------
\cventry
{Intern} % Job title
{Ixia, Keysight Technologies} % Organization
{Kolkata, India} % Location
{Dec. 2012 - Jun. 2013} % Date(s)
{\begin{cvitems} % Description(s) of tasks/responsibilities
		\item {Developed a web-based automated build management tool using Django to streamline development workflows.}
		\item {Designed and built a unit testing and mocking framework for C, supporting both user-space and kernel-space applications.}
\end{cvitems}}

	
\end{cventries}