%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Student Research Assistant} % Job title
    {IntERLab, Asian Institute Of Technology} % Organization
    {Bangkok, Thailand} % Location
    {March. 2019 - Present} % Date(s)
    {\begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Designed and developed LoRa support for "Real-Time Haze Monitoring and Forest Fire Detection Information Centric Networks (SEA\_HAZEMON@TEIN)".}
    \item {Ported embedded STM32 code to run with custom-developed LoRa module.}
    \item {LoRa gateway configurations (The Things Network, Kerlink)}
    \item {Developing Python Django application server running on docker to receive LoRa sensor data.}
      \item {Developed a React Native mobile application for "BangPun: Distributed Ledger for Rural Communities".}
      \end{cvitems}}

  \cventry
    {Freelancer} % Job title
    {Freelance} % Organization
    {Kalimpong, India} % Location
    {2017 - 2018} % Date(s)
    {\begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a web-based issue ticketing system through text messages (SMS) using Node.js, Express.js, Backbone.js, and MongoDB.}
    \item {Developed a Laravel website for a resort in Kalimpong.}
      \end{cvitems}}

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Ixia} % Organization
    {Kolkata, India} % Location
    {Jul. 2013 - Jun. 2016} % Date(s)
    {\begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Lead engineer on implementing HTTP/2 native support for "BreakingPoint".}
        \item {Worked on developing "BreakingPoint VE", the virtual edition of "Breaking Point".}
        \item {Worked on developing software virtualization of BitBlaster (L2 packet generator) and Routing Robot (L3 packet generator) modules for "BreakingPoint VE". Their implementation used FGPA in the hardware edition.}
        \item {Worked on various performance improvement strategies for "BreakingPoint VE".}
        \item {Prototyped "BreakingPoint VE" with DPDK to analyze its feasibility and performance impact.}
        \item {Improved the stability of "BreakingPoint" by fixing many bugs on the network processor.}
        \item {Deployed a docker registry, and docker scripts to host and build development environment docker images for "BreakingPoint".}
        \item {Supervised an intern in developing an internal resource reservation web-app using Django, AngularJs and Mysql.}
      \end{cvitems}}

%---------------------------------------------------------
  \cventry
    {Intern} % Job title
    {Ixia} % Organization
    {Kolkata, India} % Location
    {Dec. 2012 - Jun. 2013} % Date(s)
    {\begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and developed a web-based automated build management tool using Django which simplified package version management. It was used for many years to build the product "IxLoad".}
        \item {Designed and developed a unit test and mocking framework for C for both user-space and kernel-space. It was used internally by some packages.}
      \end{cvitems}}

\end{cventries}
